---
title: "EDA for the categorical variables"
author: "Yinqiao Wang"
output: pdf_document
---

```{r setup II, include=FALSE}
options(knitr.graphics.auto_pdf = TRUE)
knitr::opts_chunk$set(
  fig.height = 8,
  fig.width = 10,
  collapse = TRUE,
  fig.align = "center",
  dpi = 600
)
library(dplyr)
library(here)
library(tidyr)
library(ggplot2)
library(ggrepel)
library(forcats)
library(choroplethrZip)
library(ggmap)
library(zipcodeR)
```

```{r, echo=FALSE}
# Read in data sets
orders_allyears_df <- readRDS(here("intermediary_data/orders_allyears_df.rds"))
orders_allyears_plot <- orders_allyears_df %>%
  filter(POC != 'Emergency Clothing Events' & POC != 'Clothing Exchange') %>%
  filter(adult == 0)

orders_agg_Organization <- orders_allyears_plot %>%
  group_by(Organization) %>%
  mutate(`Daily served inds` = female_small + female_large + male_small + male_large) %>% 
  filter(!is.na(Organization)) %>%
  summarise(`Served individuals` = sum(`Daily served inds`)) %>%
  mutate(prop_requests = `Served individuals` / sum(`Served individuals`)) %>%
  mutate_if(is.numeric, round, 3)

orders_agg_School <- orders_allyears_plot %>%
  group_by(School) %>%
  mutate(`Daily served inds` = female_small + female_large + male_small + male_large) %>% 
  filter(!is.na(School)) %>% 
  summarise(`Served individuals` = sum(`Daily served inds`)) %>%
  mutate(prop_requests = `Served individuals` / sum(`Served individuals`)) %>%
  mutate_if(is.numeric, round, 3)

orders_agg_City <- orders_allyears_plot %>%
  group_by(City) %>%
  mutate(`Daily served inds` = female_small + female_large + male_small + male_large) %>% 
  mutate(City = replace(City, City == "#N/A", NA)) %>%
  filter(!is.na(City)) %>% 
  summarise(`Served individuals` = sum(`Daily served inds`)) %>%
  mutate(prop_requests = `Served individuals` / sum(`Served individuals`)) %>%
  mutate_if(is.numeric, round, 3)

## Read in zipcode data set
data(zip.regions)

## Load NC state and wake county's zip code
north_carolina_zip <- zip.regions$region[zip.regions$state.name == "north carolina"]
wake_zip <- zip.regions$region[zip.regions$county.name == "wake"]

## Set reference Google map API
register_google("<your API>")

orders_agg_Zip <- orders_allyears_plot %>%
  filter(!is.na(`Zip`) & `Zip` %in% north_carolina_zip) %>%
  mutate(`Daily served inds` = female_small + female_large + male_small + male_large) %>%   
  group_by(`Zip`) %>%
  summarise(num_requests = sum(`Daily served inds`)) %>%
  mutate(prop_requests = num_requests / sum(num_requests)) %>%
  mutate_if(is.numeric, round, 3)

colnames(orders_agg_Zip) = c("region", "Request numbers", "value")

orders_agg_Zip$region <- as.character(orders_agg_Zip$region)
```

# Exploratory data analysis for the categorical variables

We selected three categorical variables to explore: Organization, School, and City. We first calculated the number of individuals served by each organization/school/city. Then, based on the total number of individuals served, we calculated the proportion of service by each organization/school/city. We can find the top 10 organizations/schools/cities that mostly collaborated with the Note in the Pocket. Meanwhile, we mapped all the zipcode information except for missing value and outside North Carolina's zipcode. Combining the information from the pie chart, it is not surprising to see the Raleigh, Cary, Garner areas are the top three cities for the proportion. More service may be provided to the individuals in the Apex area, considering the influence of distance.

```{r warning=FALSE, message=FALSE, echo=FALSE}
# make a pie chart for top 5 Cities
orders_data_to_plot_City <- orders_agg_City %>%
  arrange(desc(prop_requests)) %>%
  mutate(label = case_when(row_number() <=  10 ~ City, 
                           row_number() > 10 ~ 'Other')) %>%
  group_by(label) %>%
  summarise(prop_requests = sum(prop_requests)) %>%
  arrange(desc(prop_requests))

orders_data_to_plot_City$label <- fct_inorder(orders_data_to_plot_City$label)

ggplot(orders_data_to_plot_City, aes(x = "", y = prop_requests, fill = label)) +
  geom_col(color = "black") +
  geom_text_repel(aes(x = 1.6, 
                label = scales::percent(prop_requests, accuracy = .1)), 
            position = position_stack(vjust = .5)) +
  ggtitle("Proportion of served individual number by city") +
  guides(fill = guide_legend(title = "City")) +
  scale_fill_viridis_d() +
  coord_polar(theta = "y") + 
  theme_void()

# make a pie chart for top 10 Schools
orders_data_to_plot_School <- orders_agg_School %>%
  arrange(desc(prop_requests)) %>%
  mutate(label = case_when(row_number() <=  10 ~ School, 
                           row_number() > 10 ~ 'Other')) %>%
  group_by(label) %>%
  summarise(prop_requests = sum(prop_requests)) %>%
  arrange(desc(prop_requests))

orders_data_to_plot_School$label <- fct_inorder(orders_data_to_plot_School$label)

ggplot(orders_data_to_plot_School, aes(x = "", y = prop_requests, fill = label)) +
  geom_col(color = "black") +
  geom_text_repel(aes(x = 1.6, 
                label = scales::percent(prop_requests, accuracy = .1)), 
            position = position_stack(vjust = .5)) +
  ggtitle("Proportion of served individual number by school") +
  guides(fill = guide_legend(title = "School")) +
  scale_fill_viridis_d() +
  coord_polar(theta = "y") + 
  theme_void()

# make a pie chart for top 10 organizations
orders_data_to_plot_Organization <- orders_agg_Organization %>%
  arrange(desc(prop_requests)) %>%
  mutate(label = case_when(row_number() <=  10 ~ Organization, 
                           row_number() > 10 ~ 'Other')) %>%
  group_by(label) %>%
  summarise(prop_requests = sum(prop_requests)) %>%
  arrange(desc(prop_requests))

orders_data_to_plot_Organization$label <- fct_inorder(orders_data_to_plot_Organization$label)

ggplot(orders_data_to_plot_Organization, aes(x = "", y = prop_requests, fill = label)) +
  geom_col(color = "black") +
  geom_text_repel(aes(x = 1.6, 
                label = scales::percent(prop_requests, accuracy = .1)), 
            position = position_stack(vjust = .5)) +
  ggtitle("Proportion of served individual number by organization") +
  guides(fill = guide_legend(title = "Organization")) +
  scale_fill_viridis_d() +
  coord_polar(theta = "y") + 
  theme_void()

## Mapping the proportion using zipcode
zip_choropleth(orders_agg_Zip, 
               zip_zoom = wake_zip, 
               num_colors = 6, 
               reference_map = F,
               title    = "Note in the Pocket_Request order zipcode information map",
               legend   = "Proportion of served individual\nnumber by zipcode")
```