# Request Lag Plots

Understanding the trends in the __lag time__ is the first step towards improving order turnaround speed.
The lag time is the number of days between an order being received and fulfilled.
For example, if an order was received on March 2 and fulfilled on March 10, the lag time would be 8 days.
To get view of how the lag time has changed over time, we plot lag time on the y-axis against the date the orders were received on the x-axis.
If an order was received on March 2 2020 and filled on March 10 2020 that point would show up at March 2 2020 on the x-axis with a y-value of 8.
We also stratified by gender to get a sense of if the lag time distributions was different for males and females.
Because points can over lap, e.x. two orders were received on March 2 and both were filled in 8 days, we also adjusted the transparency of the points.
A darker point means that there are actually many orders stacked at the same value.
The vertical line at March 15, 2020 is to give a general date for when COVID may have started to affect operations.


```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(lubridate)
library(here)
orders2019_df <- readRDS(here("intermediary_data/orders2019_df.rds"))
orders2020_df <- readRDS(here("intermediary_data/orders2020_df.rds"))
orders2021_df <- readRDS(here("intermediary_data/orders2021_df.rds"))
orders_df = rbind(orders2019_df, orders2020_df, orders2021_df)


recv_date = as.Date(orders_df$`Date Received`, format="%y-%m-%d")
recv_date_y = year(recv_date)
recv_date_md = recv_date
year(recv_date_md) = 2000

fill_date = as.Date(orders_df$`Date Filled`, format="%y-%m-%d")
female = (orders_df$gt != 0 | orders_df$wt != 0) & !is.na(orders_df$gt) 

date_diff = fill_date - recv_date

plot_df = data.frame(recv_date, recv_date_y, recv_date_md, date_diff, female)

ggplot(plot_df, aes(x = recv_date, y = date_diff, color)) +
  geom_point(size=2, aes(color = female), alpha = 0.5) +
  ylab("Lag Time") +
  xlab("Date Received") + 
  ggtitle("Request fulfillment lag time")  + 
  geom_vline(xintercept = as.Date("2020-03-15")) +
  scale_x_date(date_breaks="1 month", date_labels="%B-%Y")  + 
  theme(axis.text.x = element_text(face = "bold", color = "#993333", 
                                   size = 12, angle = 90)) +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "red"))
```



Next we filter out any orders that take less than 5 days to fulfill.
This helps remove emergency orders that needed immediate attention and focus on more standard orders.


```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
plot_df2 = plot_df %>% filter(date_diff >= 5)
ggplot(plot_df2, aes(x = recv_date, y = date_diff, color)) +
  geom_point(size=2, aes(color = female), alpha = 0.5) +
  ylab(" Lag Time") +
  xlab("Date Received") + 
  ggtitle("Request fulfillment lag time > 5 days")  + 
  geom_vline(xintercept = as.Date("2020-03-15")) +
  scale_x_date(date_breaks="1 month", date_labels="%B-%Y")  + 
  theme(axis.text.x = element_text(face = "bold", color = "#993333", 
                                   size = 12, angle = 90)) +
  scale_color_manual(values = c("TRUE" = "blue", "FALSE" = "red"))
```

To reduce clutter, we also plot the requests for each gender separately.

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
plot_df3 = plot_df %>% filter(female)%>% filter(date_diff >= 5)
ggplot(plot_df3, aes(x = recv_date, y = date_diff, color)) +
  geom_point(size=2, alpha = 0.5, color = "red") +
  ylab(" Lag Time") +
  xlab("Date Received") + 
  ggtitle("Request fulfillment for females")  + 
  geom_vline(xintercept = as.Date("2020-03-15")) +
  scale_x_date(date_breaks="1 month", date_labels="%B-%Y")  + 
  theme(axis.text.x = element_text(face = "bold", color = "#993333", 
                                   size = 12, angle = 90))
```


```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
plot_df4 = plot_df %>% filter(!female)%>% filter(date_diff >= 5)
ggplot(plot_df4, aes(x = recv_date, y = date_diff, color)) +
  geom_point(size=2, alpha = 0.5, color = "blue") +
  ylab(" Lag Time") +
  xlab("Date Received") + 
  ggtitle("Request fulfillment for males")  + 
  geom_vline(xintercept = as.Date("2020-03-15")) +
  scale_x_date(date_breaks="1 month", date_labels="%B-%Y")  + 
  theme(axis.text.x = element_text(face = "bold", color = "#993333", 
                                   size = 12, angle = 90))
```

The request distributions look similar for both males and females.
There is a clear spike in request fulfillment time around the onset of COVID, when Note in the Pocket had to temporarily close and volunteering was not allowed


Finally, we stack all of the data up by month.
This more easily visualizes trends that occur throughout a year.

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# stack everything on year
plot_df5 = plot_df %>% filter(date_diff >= 5)
plot_df5$recv_date_y = factor(plot_df5$recv_date_y)

ggplot(plot_df5, aes(x = recv_date_md, y = date_diff, color)) +
  geom_point(size=2, aes(color = recv_date_y), alpha = 0.25) +
  ylab(" Lag Time") +
  xlab("Date Received") + 
  ggtitle("Request fulfillment lag time stacked monthly")  + 
  scale_x_date(date_breaks="1 month", date_labels="%B")  +
  theme(axis.text.x = element_text(face = "bold", color = "#993333", 
                                   size = 12, angle = 90)) + 
  geom_smooth() + 
  scale_color_manual(values = c("2019" = "blue", "2020" = "red", "2021" = "orange"))
```


As expected, the summer months have fewer request and also less lag with requests ramping back up at the beginning of the academic year.
We can clearly see the effect of the onset of COVID at the beginning of 2020 compared to the rest of the years.
